Automatic Identification and Annotation of Parallel Tasks in Programs

### 2017-10-31 docs/ACM/paper.tex
Putting paper in ACM format.

\documentclass[pageno]{jpaper}

\newcommand{\pactedition}{26th}
\newcommand{\pactyear}{17}
\newcommand{\pactcompyear}{20\pactyear}

%replace XXX with the submission number you are given from the PACT submission site.
\newcommand{\pactsubmissionnumber}{XXX}

\usepackage[normalem]{ulem}

@@

\guido{Not sure if we should dive into a discussion of what is a regular or an irregular program; to be even more precise we are actually mining task parallelism (for this moment) only within loops; hence I propose this new title}
\pedro{I think we should say "Automatic Mining of Task Parallelism in Programs" because we might mine task parallelism in recursive functions as well.}
\title{\rmv{Task Mining in Irregular Programs.}\new{Automatic Mining of Task Parallelism in Programs}}

\date{}
\maketitle

\thispagestyle{empty}

@@

@@

\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
\bibliographystyle{IEEEtranS}
\bibliography{references}

>>>>

%% For double-blind review submission
\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

\makeatletter\if@ACM@journal\makeatother

%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\acmMonth{1}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother

%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[PL'17]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2017}{New York, NY, USA}
\acmYear{2017}
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

\newcommand{\fer}[1]{\textcolor{red}{#1}}

%% For review submission
\setcopyright{none}

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}

%% Packages that we are using in this version of the work:
\usepackage{hyperref}

@@

\title[Automatic Identification and Annotation of Parallel Tasks in Programs]
{Automatic Identification and Annotation of Parallel Tasks in Programs}

\author{Pedro Henrique Ramos Costa}
\authornote{with author1 note}          %% \authornote is optional;
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Researcher}
  \department{DCC}
  \institution{UFMG}
  \streetaddress{6627 Antonio Carlos Avenue}
  \city{Belo Horizonte}
  \state{Minas Gerais}
  \postcode{31.270-213}
  \country{Brazil}
}
\email{pedroramos@dcc.ufmg.br}

\author{Gleison Souza Diniz Mendonc\c{c}a}
\authornote{with author1 note}          %% \authornote is optional;
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Researcher}
  \department{DCC}
  \institution{UFMG}
  \streetaddress{6627 Antonio Carlos Avenue}
  \city{Belo Horizonte}
  \state{Minas Gerais}
  \postcode{31.270-213}
  \country{Brazil}
}
\email{gleison.mendonca@dcc.ufmg.br}

\author{Divino C\'{e}sar}
\authornote{with author1 note}
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Researcher}
  \department{IC}
  \institution{UNICAMP}
  \streetaddress{Cidade Universit\'{a}ria}
  \city{Campinas}
  \state{S\~{a}o Paulo}
  \postcode{13083-970}
  \country{Brazil}
}
\email{divcesar@gmail.com}

\author{Guido Ara\'{u}jo}
\authornote{with author1 note}
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Professor}
  \department{IC}
  \institution{UNICAMP}
  \streetaddress{Cidade Universit\'{a}ria}
  \city{Campinas}
  \state{S\~{a}o Paulo}
  \postcode{13083-970}
  \country{Brazil}
}
\email{guido@ic.unicamp.br}

\author{Fernando Magno Quint\~{a}o Pereira}
\authornote{with author1 note}
\orcid{nnnn-nnnn-nnnn-nnnn}
\affiliation{
  \position{Professor}
  \department{DCC}
  \institution{UFMG}
  \streetaddress{6627 Antonio Carlos Avenue}
  \city{Belo Horizonte}
  \state{Minas Gerais}
  \postcode{31.270-213}
  \country{Brazil}
}
\email{fernando@dcc.ufmg.br}          %% \email is recommended

@@

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011041</concept_id>
<concept_desc>Software and its engineering~Compilers</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011008.10011024.10011035</concept_id>
<concept_desc>Software and its engineering~Procedures, functions and subroutines</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003766.10003776</concept_id>
<concept_desc>Theory of computation~Regular languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003752.10010124.10010131.10010134</concept_id>
<concept_desc>Theory of computation~Operational semantics</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Compilers}
\ccsdesc[300]{Software and its engineering~Procedures, functions and subroutines}
\ccsdesc[300]{Theory of computation~Regular languages}
\ccsdesc[300]{Theory of computation~Operational semantics}

\keywords{Parallelism, Tasks, OpenMP}

\maketitle

@@

\bibliography{references}
